Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments

### 2021-09-20 doc/paper.Rmd
export fig for graphical abstract
update data availability statement

We thank Collin Edwards, Andrew Mercadante, Ellie McDaniel and 3 anonymous reviewers for helpful discussions and comments on the manuscript.
We also thank the technicians and students who helped conduct the *Heliconia* censuses and the BDFFP and INPA for logistical support.
Financial support was provided by the U.S.
National Science Foundation (awards DEB-0614339, DEB-0614149, INT 98-06351, and DEB-1948607).
This is publication No. \_\_\_ in the BDFFP Technical Series.
The authors delcare no conflicts of interest.

@@

Data used in this study are available at the Dryad Digital Repository [links included upon acceptance]; R code for analyses and visualizations are archived with Zenodo at <https://doi.org/10.5281/zenodo.5364591>.

@@

>>>>

We thank Collin Edwards, Andrew Mercadante, Ellie McDaniel and 3 anonymous reviewers for helpful discussions and comments on the manuscript.
We also thank the technicians and students who helped conduct the *Heliconia* censuses and the BDFFP and INPA for logistical support.
Financial support was provided by the U.S.
National Science Foundation (awards DEB-0614339, DEB-0614149, INT 98-06351, and DEB-1948607).
This is publication No. 824 in the BDFFP Technical Series.
The authors delcare no conflicts of interest.

@@

All data and code for analyses and visualizations are archived with Zenodo at <https://doi.org/10.5281/zenodo.5364591>.

@@

<!-- For graphical abstract -->

```{r}
agg_tiff(here::here("doc", "figures", "surv-spei_graphical-abstract.tiff"),
        width = 7, height = 8, units = "in", res = 300)
tar_read(s_spei_plot) & theme(text = element_text(size = 14))
invisible(dev.off())
```
